Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-07-29 main.Rmd
intro of which harmonies to show changed

\noindent The data structure suggests that we look at pairs of cyclic granularities at a time from $N_C$ cyclic granularities. Hence, all possible pairs of cyclic time granularities that could be analyzed together is $^{N_C} P_2$, with each of the circular granularity either mapped to facets or x-axis. Now, if $N_C$ is fairly large, even after excluding clashes, the list of harmonies left would be very large and overwhelming for human consumption. Hence, there is a need to rank these harmonies basis how well they capture the variation in the measured variable.<!--The harmony pairs $(C_i, C_j)$ with higher average variation in the measured variable between different levels of $C_i$ and $C_j$ has a higher chance to bring out distinct characteristics of the data.<!-- Ranking could be based on how well a harmony pair displays the variation in distributions of the measured variable within and across each levels of the cyclic granularities. For each facet level, the most interesting display is the one in which the difference in the distribution of the measured variable between the x-axis categories is maximum. The harmony pair which has more variation between x-axis levels for all facet levels, on average, is likely to be a good measure of how important a harmony pair is displaying variation in the distributions. -->

>>>>

\noindent The data structure suggests that we look at pairs of cyclic granularities at a time from $N_C$ cyclic granularities. Hence, all possible pairs of cyclic time granularities that could be analyzed together is $^{N_C} P_2$, with each of the circular granularity either mapped to facets or x-axis. Now, if $N_C$ is fairly large, even after excluding clashes, the list of harmonies left would be very large and overwhelming for human consumption. Hence, there is a need to select only those harmonies which have significant variation in the measured variable and hence might appear to be interesting when displayed. Moreover, there is a need to rank these harmonies basis how interesting they are, which could be measured through the captured amount of variation in the measured variable.<!--The harmony pairs $(C_i, C_j)$ with higher average variation in the measured variable between different levels of $C_i$ and $C_j$ has a higher chance to bring out distinct characteristics of the data.<!-- Ranking could be based on how well a harmony pair displays the variation in distributions of the measured variable within and across each levels of the cyclic granularities. For each facet level, the most interesting display is the one in which the difference in the distribution of the measured variable between the x-axis categories is maximum. The harmony pair which has more variation between x-axis levels for all facet levels, on average, is likely to be a good measure of how important a harmony pair is displaying variation in the distributions. -->
